\TitlePt

### 2016-03-30 paper-fatiando.tex
Emphasize that Fatiando is growing and started in my PhD in conclusion

The biggest challenge that \textit{Fatiando a Terra} faces in the near future is
the development of a user and, consequently, a developer community. This
is a key part for the survival of any open-source project.

>>>>

The project was started as part of my PhD thesis work but grew beyond this
context.  The development is on-going and recently new collaborators from
outside of Brazil have started contributing code to the project.  The biggest
challenge that \textit{Fatiando a Terra} faces in the near future is the
development of a strong user and, consequently, a developer community. This is
a key part for the survival of any open-source project.
